TacticToe: Learning to Prove with Tactics

### 2018-02-22 tactictoe_jv.tex
fix typo
minor

  In this work, we develop in the ITP \holfour a procedure to select suitable
  tactics depending on the current proof state by learning
  from previous proofs. Backed by this machine-learned guidance, our prover
  \tactictoe relies on \emph{Monte
  Carlo tree search}~\cite{montecarlo} to find sequences of tactic applications
  leading to an ITP proof.
  To this end, we \emph{extract and record} tactic invocations from the ITP
  proofs (Section~\ref{sec:recording}) and
  \emph{build efficient machine learning classifiers} based on such training
  examples (Section~\ref{s:prediction}).  The learned data serves as
  guidance for the Monte Carlo tree search that explores different
  proof paths (Section~\ref{sec:proofsearch}). The result, if
  successful, is a verified human-level proof composed of \holfour
  tactics (Section~\ref{sec:proofdisplay}). We evalute the system on a large
  set of theorems originating
  from \holfour (Section~\ref{s:experiments}).

@@

\begin{definition}\label{def:stree}(search tree)\\
A search tree $\mathfrak{T}$ is a sixtuple
$(\mathbb{T},\mathbb{G},\mathbb{A},T,G,A)$
that respects the following conditions:
\begin{itemize}
\item $\mathbb{T}$ is a set of tactics, $\mathbb{G}$ is a set of goals
 and $\mathbb{A}$ is a set of nodes representing lists of goals.
\item $T$ is a function from $\mathbb{G}$ to $\mathcal{P}(\mathbb{T})$. It
takes a goal and return the set of tactics already applied to this goal.
\item $G$ is a total function from $\mathbb{A}$ to $\mathcal{P}(\mathbb{G})$.
It takes a node and returns the list of goals of this node.
\item $A$ is a partial function from $\mathbb{G} \times \mathbb{T}$ to
$\mathbb{A}$. Its support $\mathit{Support}(A)$ is 
$\lbrace (g,t) \in \mathbb{G} \times \mathbb{T}\ |\ t \in T(g)
\rbrace$. And if $(g,t) \in \mathit{Support}(A)$, then $t(g) = G(A(g,t))$. In 
other words, the output $t(g)$ is exactly the list
of goals contained in the node produced by $A$ from $(g,t)$.
\item It is acyclic, i.e. a node cannot be a descendant (see 
Definition~\ref{def:desc}) of itself.
\item There is exactly one node with no parents. This root node contains 
exactly one goal which is the initial goal (also called conjecture).
\end{itemize}

>>>>

  In this work, we develop in the ITP \holfour a procedure to select suitable
  tactics depending on the current proof state by learning
  from previous proofs. Backed by this machine-learned guidance, our prover
  \tactictoe relies on \emph{Monte
  Carlo tree search}~\cite{montecarlo} to find sequences of tactic applications
  leading to an ITP proof.
  To this end, we \emph{extract and record} tactic invocations from the ITP
  proofs (Section~\ref{sec:recording}) and
  \emph{build efficient machine learning classifiers} based on such training
  examples (Section~\ref{s:prediction}).  The learned data serves as
  guidance for the Monte Carlo tree search that explores different
  proof paths (Section~\ref{sec:proofsearch}). The result, if
  successful, is a verified human-level proof composed of \holfour
  tactics (Section~\ref{sec:proofdisplay}). We evaluate the system on a large
  set of theorems originating
  from \holfour (Section~\ref{s:experiments}).

@@

\begin{definition}\label{def:stree}(search tree)\\
A search tree $\mathfrak{T}$ is a sixtuple
$(\mathbb{T},\mathbb{G},\mathbb{A},T,G,A)$
that respects the following conditions:
\begin{itemize}
\item $\mathbb{T}$ is a set of tactics, $\mathbb{G}$ is a set of goals
 and $\mathbb{A}$ is a set of nodes representing lists of goals.
\item $T$ is a function from $\mathbb{G}$ to $\mathcal{P}(\mathbb{T})$. It
takes a goal and return the set of tactics already applied to this goal.
\item $G$ is a total function from $\mathbb{A}$ to $\mathcal{P}(\mathbb{G})$.
It takes a node and returns the list of goals of this node.
\item $A$ is a partial function from $\mathbb{G} \times \mathbb{T}$ to
$\mathbb{A}$. Its support $\mathit{Support}(A)$ is 
$\lbrace (g,t) \in \mathbb{G} \times \mathbb{T}\ |\ t \in T(g)
\rbrace$. And if $(g,t) \in \mathit{Support}(A)$, then $t(g) = G(A(g,t))$. In 
other words, the output $t(g)$ is exactly the list
of goals contained in the node produced by $A$ from $(g,t)$.
\item It is acyclic, i.e. a node cannot be a strict descendant (see 
Definition~\ref{def:desc}) of itself.
\item There is exactly one node with no parents. This root node contains 
exactly one goal which is the initial goal (also called conjecture).
\end{itemize}
